Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-08-18 write-up/covid-writeup.tex
updating prev figures

\textcolor{red}{
While the model-based estimates appear more reasonable, note that the estimate on the last week of April is XX\% which is a severe underestimate. Caution is therefore warranted when interpreting these estimates.  We know that the age-specific infection fatality rate is likely time-varying and may vary by other factors beyond age.  Therefore, improvements could be made by more finely grained, and accurate IFR estimates; however, there is currently minimal publicly available data to do so.  Moreover, the (thankfully) low number of deaths per strata make uncertainty in these estimates quite high.  The 95\% credible range for active infections on April 25th, for example, is $[XX,XX]$ with a posterior mean of $XX$.  Finally, the doubly robust estimates appear similar to the IPW estimate.
}

>>>>

\textcolor{red}{
While the model-based estimates appear more reasonable, note that the estimate on the last week of April is 0.25\% which is a severe underestimate. Caution is therefore warranted when interpreting these estimates.  We know that the age-specific infection fatality rate is likely time-varying and may vary by other factors beyond age.  Therefore, improvements could be made by more finely grained, and accurate IFR estimates; however, there is currently minimal publicly available data to do so.  Moreover, the (thankfully) low number of deaths per strata make uncertainty in these estimates quite high.  Finally, the doubly robust estimates appear similar to the IPW estimate.
}
